Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-04-28 manuscript/manuscript.Rmd
:pen:

\begin{equation}
\label{hopf}
\end{equation}

@@

A yet more difficult forecasting scenario is created by the saddle-node bifurcation.
May's consumer-resource model is a one-dimensional model describing the growth of a 'resource' population (e.g. herbivore) which is grazed by a consumer [@May1979].
As in the Nicholson-Bailey model, in the absence of that predation the resource population density grows under a density-dependent pattern described by a logistic function.
Meanwhile, the resource population is also grazed by a consumer at a rate given by a Holling type III s-curve (typically used to model handling time).

>>>>

\begin{align}
H_{t+1} &= H_t \exp \left( r \left(1 - \tfrac{H}{K}\right) - c P_t + \eta_{H,t}
P_{t+1} &= H_t \exp \left( r \left(1  \tfrac{H}{K}\right) \right)  \left(1 -  \exp \left(- c P_t + \eta_{P,t}\right) \right)
\label{hopf}
\end{align}

@@

A yet more difficult forecasting scenario is created by the saddle-node bifurcation.
May's consumer-resource model is a one-dimensional model describing the growth of a 'resource' population (e.g. herbivore) which is grazed by a consumer [@May1979].
As in the Nicholson-Bailey model, in the absence of that predation the resource population density grows under a density-dependent pattern described by a logistic function.
The resource population is also grazed by a consumer at a rate given by a Holling type III s-curve (typically used to model handling time). 
For a certain range of parameter choices, this model supports alternative stable state dynamics, and this model has been identified and employed in explaining alternative stable state dynamics in a broad range ecological and socio-ecological systems [@Scheffer2001].

\begin{align}
\end{align}

If the environment slowly alters one of the parameters (say, the encounter efficiency, `a`, in our formulation), one of the stable nodes moves closer and closer to the unstable saddle point, leading to a bifurcation that destroys the stable state, leaving the system to suddenly transition to the alternative stable state.
Saddle-node bifurcations (also known as fold bifurcations) also create a phenomenon known as hysteresis, where it is not sufficient to restore the environment to the previous parameter values to recover the previous state. 
Unlike the Hopf bifurcation which exhibits a continuous transition from a stable node to a small limit cycle that then grows, the saddle-node transition is a discontinuous or so-called 'catastrophic' bifurcation.
Due both this sudden, catastrophic nature of the transition and the difficulty in reversing the shift after it has occurred, saddle-node bifurcations have become a nearly ubiquitous [@Scheffer2009]

Saddle-node b
